Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Added link to benchmarks on anonymous Google Drive.
Added full benchmark environment, with generated logs, into an archive and
shared on a Google Drive.

The
synthesized controllers were confirmed to be stable outside of our model
representation using MATLAB, positively answering RQ2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote.\footnote{\url{url.here.}}

>>>>

The
synthesized controllers were confirmed to be stable outside of our model
representation using MATLAB, positively answering RQ2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}
